Title Goes Here

### 2020-01-29 paper/paper.tex
Example for paper

%%
%% This is file `sample-acmsmall.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `acmsmall')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-acmsmall.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[acmsmall]{acmart}
\usepackage{booktabs}

@@

@@

>>>>

%%
%% This is file `sample-acmsmall.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `acmsmall')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-acmsmall.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[acmsmall]{acmart}
\usepackage{booktabs}
\usepackage{listings}

\lstset{language=haskell, deletekeywords={abs}}

@@

\subsection{Translation Example} % TODO: Does it make sense for this to be a
                                 % subsection of the intro?

In the example below, \texttt{example} would get transformed into \texttt{example'}:

\begin{lstlisting}
import Data.Char (ord)

x :: Either Char Int
x = Left 'a'

example :: Int
example =
  case x of
    Left  c -> ord c
    Right i -> i

example' :: Int
example' =
  abs (CaseExp (rep x)
               (SumMatch (OneProdMatch (\c -> ord c))
                         (OneSumMatch
                           (OneProdMatch (\i -> i)))))
\end{lstlisting}

@@

[Remove metadata from Generic representation and turn tree-like structure into a list-like structure]
